---
title: "Claim Counts Prediction Using Individual Data"
author: "Gabriele Pittarello"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Claim Counts Prediction Using Individual Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eval=FALSE, include=TRUE}
library(ReSurv)
library(reticulate)
use_virtualenv("pyresurv")
library(ggplot2)
```


In this vignette we show a pipeline for predicting individual claim counts using the `ReSurv` package. 

This vignette was created for the *2024 Reserving Call Paper Program on Technology and the Reserving Actuary* of the Casualty Actuarial Society (CAS) and the CAS Reserves Working Group. We would like to thank the team of reviewers that provided feedback that improved our package.

# Installation

To install the developer version of the `ReSurv` package.

```{r eval=FALSE, include=TRUE}
library(devtools)
devtools::install_github("edhofman/resurv")
library(ReSurv)
packageVersion("ReSurv")

```


To handle the Python dependencies for *the first package installation*, we suggest to create a dedicated virtual environment. The remaining part of this Section can be disregard from users that are not interested in using our models based on Neural Networks.

```{r eval=FALSE, include=TRUE}
ReSurv::install_pyresurv()
```

The default name of the virtual environment is `"pyresurv"`.

We then suggest to refresh the R session and to import the `ReSurv` package in R using 

```{r eval=FALSE, include=TRUE}
library(ReSurv)
reticulate::use_virtualenv("pyresurv")

```

## Managing Multiple Package Dependencies

For the case of multiple packages using isolated-package-environments we suggest the following procedure. Below an example for `pysparklyr`.

```{r eval=FALSE, include=TRUE}
envname <- "./venv"
ReSurv::install_pyresurv(envname = envname)
pysparklyr::install_pyspark(envname = envname)
```

# Data Simulation

We simulate a synthetic data set from scenario Alpha.

```{r eval=FALSE, include=TRUE}
input_data <- data_generator(random_seed = 7,
                             scenario = "alpha",
                             time_unit = 1 / 360,
                             years = 4,
                             period_exposure = 200)
```

We inspect the data set.

```{r eval=FALSE, include=TRUE}
str(input_data)
```


# Data Pre-Processing

The data is pre-processed using the `IndividualDataPP` function.

```{r eval=FALSE, include=TRUE}
individual_data <- IndividualDataPP(data = input_data,
                                    categorical_features = "claim_type",
                                    continuous_features = "AP",
                                    accident_period = "AP",
                                    calendar_period = "RP",
                                    input_time_granularity = "days",
                                    output_time_granularity = "quarters",
                                    years = 4)

```

# Selection of the hyper-parameters


This Sections first shows the usage of the `ReSurvCV` function for cross-validation. Secondly, we show how to combine the `ReSurvCV` function into the `ParBayesianOptimization`package routine for performing the Bayesian Optimization of Hyperparameters.

## XGB: K-Fold cross-validation (CV)


Example of K-Fold cross-validation (CV) for the XGB model.

```{r eval=FALSE, include=TRUE}

resurv_cv_xgboost <- ReSurvCV(IndividualDataPP = individual_data,
                              model = "XGB",
                              hparameters_grid = list(booster = "gbtree",
                                                      eta = c(.001),
                                                      max_depth = c(3),
                                                      subsample = c(1),
                                                      alpha = c(0),
                                                      lambda = c(0),
                                                      min_child_weight = c(.5)),
                              print_every_n = 1L,
                              nrounds = 1,
                              verbose = FALSE,
                              verbose.cv = TRUE,
                              early_stopping_rounds = 1,
                              folds = 5,
                              parallel = TRUE,
                              ncores = 2,
                              random_seed = 1)

```

## NN: K-Fold cross-validation

Example of K-Fold cross-validation (CV) for the NN model.

```{r eval=FALSE, include=TRUE}
resurv_cv_nn <- ReSurvCV(IndividualDataPP = individual_data,
                         model = "NN",
                         hparameters_grid = list(num_layers = c(1, 2),
                                                 num_nodes = c(2, 4),
                                                 optim = "Adam",
                                                 activation = "ReLU",
                                                 lr = .5,
                                                 xi = .5,
                                                 eps = .5,
                                                 tie = "Efron",
                                                 batch_size = as.integer(5000),
                                                 early_stopping = "TRUE",
                                                 patience = 20),
                         epochs = as.integer(300),
                         num_workers = 0,
                         verbose = FALSE,
                         verbose.cv = TRUE,
                         folds = 3,
                         parallel = FALSE,
                         random_seed = as.integer(Sys.time()))
```


## ReSurv and Bayesian Parameters Optimisation


### XGB: Bayesian Parameters Optimisation

Example of Bayesian Optimization of Hyperparameters for the XGB model.

```{r eval=FALSE, include=TRUE}

bounds <- list(eta = c(0, 1),
               max_depth = c(1L, 25L),
               min_child_weight = c(0, 50),
               subsample = c(0.51, 1),
               lambda = c(0, 15),
               alpha = c(0, 15))


obj_func <- function(eta,
                     max_depth,
                     min_child_weight,
                     subsample,
                     lambda,
                     alpha) {

  xgbcv <- ReSurvCV(
    IndividualDataPP = individual_data,
    model = "XGB",
    hparameters_grid = list(
      booster = "gbtree",
      eta = eta,
      max_depth = max_depth,
      subsample = subsample,
      alpha = lambda,
      lambda = alpha,
      min_child_weight = min_child_weight
    ),
    print_every_n = 1L,
    nrounds = 500,
    verbose = FALSE,
    verbose.cv = TRUE,
    early_stopping_rounds = 30,
    folds = 3,
    parallel = FALSE,
    random_seed = as.integer(Sys.time())
  )

  lst <- list(Score = -xgbcv$out.cv.best.oos$test.lkh,
              train.lkh = xgbcv$out.cv.best.oos$train.lkh)

  return(lst)
}



bayes_out <- bayesOpt(FUN = obj_func,
                      bounds = bounds,
                      initPoints = 50,
                      iters.n = 1000,
                      iters.k = 50,
                      otherHalting = list(timeLimit = 18000))

```


### NN: Bayesian Parameters Optimisation

Example of Bayesian Optimization of Hyperparameters for the XGB model.

```{r eval=FALSE, include=TRUE}
bounds <- list(num_layers = c(2L, 10L),
               num_nodes = c(2L, 10L),
               optim = c(1L, 2L),
               activation = c(1L, 2L),
               lr = c(0.005, 0.5),
               xi = c(0, 0.5),
               eps = c(0, 0.5))


obj_func <- function(num_layers,
                     num_nodes,
                     optim,
                     activation,
                     lr,
                     xi,
                     eps) {

  optim <- switch(optim,
                  "Adam",
                  "SGD")

  activation <- switch(activation, "LeakyReLU", "SELU")
  batch_size <- as.integer(5000L)
  number_layers <- as.integer(num_layers)
  num_nodes <- as.integer(num_nodes)

  deepsurv_cv <- ReSurvCV(IndividualData = individual_data,
                          model = "NN",
                          hparameters_grid = list(num_layers = number_layers,
                                                  num_nodes = num_nodes,
                                                  optim = optim,
                                                  activation = activation,
                                                  lr = lr,
                                                  xi = xi,
                                                  eps = eps,
                                                  tie = "Efron",
                                                  batch_size = batch_size,
                                                  early_stopping = "TRUE",
                                                  patience  = 20),
                          epochs = as.integer(300),
                          num_workers = 0,
                          verbose = FALSE,
                          verbose.cv = TRUE,
                          folds = 3,
                          parallel = FALSE,
                          random_seed = as.integer(Sys.time()))


  lst <- list(Score = -deepsurv_cv$out.cv.best.oos$test.lkh,
              train.lkh = deepsurv_cv$out.cv.best.oos$train.lkh)

  return(lst)
}

bayes_out <- bayesOpt(FUN = obj_func,
                      bounds = bounds,
                      initPoints = 50,
                      iters.n = 1000,
                      iters.k = 50,
                      otherHalting = list(timeLimit = 18000))

```


# Estimation 

In this Section we show the usage of the `ReSurv` method for the estimation of our models parameters. The hyperparameters for NN and XGB were derived with the Bayesian Optimisation procedure.

## COX

```{r eval=FALSE, include=TRUE}

resurv_fit_cox <- ReSurv(individual_data,
                     hazard_model = "COX",simplifier = TRUE)

```

## XGB

```{r eval=FALSE, include=TRUE}
hparameters_xgb <- list(
  params = list(
    booster = "gbtree",
    eta = 0.9611239,
    subsample = 0.62851,
    alpha = 5.836211,
    lambda = 15,
    min_child_weight = 29.18158,
    max_depth = 1
  ),
  print_every_n = 0,
  nrounds = 3000,
  verbose = FALSE,
  early_stopping_rounds = 500
)


resurv_fit_xgb <- ReSurv(individual_data,
                         hazard_model = "XGB",
                         hparameters = hparameters_xgb)

```

## NN

```{r eval=FALSE, include=TRUE}

hparameters_nn = list(num_layers= 2,
            early_stopping= TRUE,
            patience=350,
            verbose=FALSE,
            network_structure=NULL,
            num_nodes= 10,
            activation ="LeakyReLU",
            optim ="SGD",
            lr =0.02226655,
            xi=0.4678993,
            epsilon= 0,
            batch_size= 5000L,
            epochs= 5500L,
            num_workers= 0,
            tie="Efron" )


resurv_fit_nn <- ReSurv(individual_data,
                     hazard_model = "NN",
                     hparameters = hparameters_nn)


```


# Prediction

In this Section we show how to use our models for predictions with the `predict` method and for different output time granularities (quarterly, yearly and monthly). The output can be displayed using the methods `summary` and `print`.


```{r eval=FALSE, include=TRUE}
resurv_fit_predict_q <- predict(resurv_fit_cox)

individual_data_y <- IndividualDataPP(input_data,
                                      id = "claim_number",
                                      continuous_features = "AP_i",
                                      categorical_features = "claim_type",
                                      accident_period = "AP",
                                      calendar_period = "RP",
                                      input_time_granularity = "days",
                                      output_time_granularity = "years",
                                      years = 4,
                                      continuous_features_spline = NULL,
                                      calendar_period_extrapolation = FALSE)

resurv_fit_predict_y <- predict(resurv_fit_cox,
                                newdata = individual_data_y,
                                grouping_method = "probability")

individual_data_m <- IndividualDataPP(input_data,
                                      id = "claim_number",
                                      continuous_features = "AP_i",
                                      categorical_features = "claim_type",
                                      accident_period = "AP",
                                      calendar_period = "RP",
                                      input_time_granularity = "days",
                                      output_time_granularity = "months",
                                      years = 4,
                                      continuous_features_spline = NULL,
                                      calendar_period_extrapolation = FALSE)

resurv_fit_predict_m <- predict(resurv_fit_cox,
                                newdata = individual_data_m,
                                grouping_method = "probability")



model_s <- summary(resurv_fit_predict_y)
print(model_s)

```


Similar functions for the other models

```{r eval=FALSE, include=TRUE}
resurv_predict_xgb <- predict(resurv_fit_xgb)
resurv_predict_nn <- predict(resurv_fit_nn)
```

# Plot the predicted development factors 

In this Section we show an example of development factors plot for the COX model.

```{r eval=FALSE, include=TRUE}

resurv_fit_predict_q$long_triangle_format_out$output_granularity %>% 
    filter(AP_o==15 & claim_type == 1) %>% 
    filter(row_number()==1) %>%
    select(group_o)

plot(resurv_fit_predict_q, 
         granularity = "output",
         title_par = "COX: Accident Quarter 15 Claim Type 1",
         group_code = 30)

```

# CRPS

In this Section we show the CRPS calculation using the `survival_crps` method.

```{r eval=FALSE, include=TRUE}
crps <- survival_crps(resurv_fit_cox)
m_crps <- mean(crps$crps)
m_crps

```

# Plot the development factors

We first extract the output group code for an arbitrary group.

```{r eval=FALSE, include=TRUE}
resurv_fit_predict_q$long_triangle_format_out$output_granularity %>% 
    filter(AP_o==15 & claim_type == 1) %>% 
    filter(row_number()==1) %>%
    select(group_o)
```


We use the group code to plot the feature dependent development factors.

```{r eval=FALSE, include=TRUE}
plot(resurv_fit_predict_q, 
         granularity = "output",
         title_par = "COX: Accident Quarter 15 Claim Type 1",
         group_code = 30)

```


# Appendix

## Code to replicate Figure 1

```{r eval=FALSE, include=TRUE}
p1 <- input_data %>%
  as.data.frame() %>%
  mutate(claim_type = as.factor(claim_type)) %>%
  ggplot(aes(x = RT - AT, color = claim_type)) +
  stat_ecdf(size = 1) +
  labs(title = "", x = "Notification delay (in days)", y = "ECDF") +
  xlim(0.01, 1500) +
  scale_color_manual(
    values = c("royalblue", "#a71429"),
    labels = c("Claim type 0", "Claim type 1")
  ) +
  scale_linetype_manual(values = c(1, 3),
                        labels = c("Claim type 0", "Claim type 1")) +
  guides(
    color = guide_legend(
      title = "Claim type",
      override.aes = list(
        color = c("royalblue", "#a71429"),
        linewidth = 2
      )
    ),
    linetype = guide_legend(
      title = "Claim type",
      override.aes = list(linetype = c(1, 3), linewidth = 0.7)
    )
  ) +
  theme_bw() +
  theme(
    axis.text = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.title.x  = element_text(size = 20),
    legend.text = element_text(size = 20)
  )
p1


p2 <- input_data %>%
  as.data.frame() %>%
  mutate(claim_type = as.factor(claim_type)) %>%
  ggplot(aes(x = claim_type, fill = claim_type)) +
  geom_bar() +
  scale_fill_manual(
    values = c("royalblue", "#a71429"),
    labels = c("Claim type 0", "Claim type 1")
  ) +
  guides(fill = guide_legend(title = "Claim type")) +
  theme_bw() +
  labs(title = "", x = "Claim Type", y = "") +
  theme(
    axis.text = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    axis.title.x  = element_text(size = 20),
    legend.text = element_text(size = 20)
  )
p2


```

## Code for plotting Figure 3
Chain-Ladder case.

```{r eval=FALSE, include=TRUE}

clmodel <- resurv_fit_cox$IndividualDataPP$training.data %>%
  mutate(DP_o = 16 -
           DP_rev_o + 1) %>%
  group_by(AP_o, DP_o) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(AP_o) %>%
  arrange(DP_o) %>%
  mutate(I_cum = cumsum(I), I_cum_lag = lag(I_cum, default = 0)) %>%
  ungroup() %>%
  group_by(DP_o) %>%
  reframe(df_o = sum(I_cum * (
    AP_o <= max(resurv_fit_cox$IndividualDataPP$training.data$AP_o) - DP_o +
      1
  )) /
    sum(I_cum_lag * (
      AP_o <= max(resurv_fit_cox$IndividualDataPP$training.data$AP_o) - DP_o +
        1
    )),
  I = sum(I * (
    AP_o <= max(resurv_fit_cox$IndividualDataPP$training.data$AP_o) - DP_o
  ))) %>%
  mutate(DP_o_join = DP_o - 1) %>%
  as.data.frame()


clmodel %>%
  filter(DP_o > 1) %>%
  ggplot(aes(x = DP_o, y = df_o)) +
  geom_line(linewidth = 2.5,
            color = "#454555") +
  scale_x_continuous(breaks = c(3,5,7,9,11,13,15))+
  labs(title = "Chain ladder",
       x = "Development quarter",
       y = "Development factor") +
  ylim(1, 3. + .01) +
  theme_bw(base_size = rel(5)) +
  theme(plot.title = element_text(size = 20))

##

clmodel_months <- individual_data_m$training.data %>%
  mutate(DP_o = 48 -
           DP_rev_o + 1) %>%
  group_by(AP_o, DP_o) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(AP_o) %>%
  arrange(DP_o) %>%
  mutate(I_cum = cumsum(I), I_cum_lag = lag(I_cum, default = 0)) %>%
  ungroup() %>%
  group_by(DP_o) %>%
  reframe(df_o = sum(I_cum * (
    AP_o <= max(individual_data_m$training.data$AP_o) - DP_o + 1
  )) /
    sum(I_cum_lag * (
      AP_o <= max(individual_data_m$training.data$AP_o) - DP_o + 1
    )),
  I = sum(I * (
    AP_o <= max(individual_data_m$training.data$AP_o) - DP_o
  ))) %>%
  mutate(DP_o_join = DP_o - 1) %>%
  as.data.frame()

ticks_at <- c(4,8,12,16)*3
labels_as <- as.character(ticks_at)

clmodel_months %>%
  filter(DP_o > 1) %>%
  ggplot(aes(x = DP_o,
             y = df_o)) +
  geom_line(linewidth = 2.5,
            color = "#454555") +
  labs(title = "Chain ladder",
       x = "Development month",
       y = "Development factor") +
  ylim(1, 2.5 + .01) +
  scale_x_continuous(breaks = ticks_at, labels = labels_as) +
  theme_bw(base_size = rel(5)) +
  theme(plot.title = element_text(size = 20))


##

clmodel_years <- individual_data_y$training.data %>%
  mutate(DP_o = 4 -
           DP_rev_o + 1) %>%
  group_by(AP_o, DP_o) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(AP_o) %>%
  arrange(DP_o) %>%
  mutate(I_cum = cumsum(I), I_cum_lag = lag(I_cum, default = 0)) %>%
  ungroup() %>%
  group_by(DP_o) %>%
  reframe(df_o = sum(I_cum * (
    AP_o <= max(individual_data_m$training.data$AP_o) - DP_o + 1
  )) /
    sum(I_cum_lag * (
      AP_o <= max(individual_data_m$training.data$AP_o) - DP_o + 1
    )),
  I = sum(I * (
    AP_o <= max(individual_data_m$training.data$AP_o) - DP_o
  ))) %>%
  mutate(DP_o_join = DP_o - 1) %>%
  as.data.frame()

ticks_at <- c(3) 
labels_as <- as.character(ticks_at)

clmodel_years %>%
  filter(DP_o > 1) %>%
  ggplot(aes(x = DP_o,
             y = df_o)) +
  geom_line(linewidth = 2.5,
            color = "#454555") +
  labs(title = "Chain ladder",
       x = "Development year",
       y = "Development factor") +
  ylim(1, 2.5 + .01) +
  scale_x_continuous(breaks = ticks_at, labels = labels_as) +
  theme_bw(base_size = rel(5)) +
  theme(plot.title = element_text(size = 20))

```

COX, quarterly output.

```{r eval=FALSE, include=TRUE}
ct <- 0
ap <- 12

resurv_fit_predict_q$long_triangle_format_out$output_granularity %>%
  filter(AP_o == ap & claim_type == ct) %>%
  filter(row_number() == 1) %>%
  select(group_o)

plot(
  resurv_fit_predict_q,
  granularity = "output",
  title_par = "COX: Accident Quarter 12 Claim Type 0",
  group_code = 23
)


ct <- 0
ap <- 36

resurv_fit_predict_m$long_triangle_format_out$output_granularity %>%
  filter(AP_o == ap & claim_type == ct) %>%
  filter(row_number() == 1) %>%
  select(group_o)

plot(
  resurv_fit_predict_m,
  granularity = "output",
  color_par = "#a71429",
  title_par = "COX: Accident Month 36 Claim Type 0",
  group_code = 71
)



ct <- 1
ap <- 7

resurv_fit_predict_m$long_triangle_format_out$output_granularity %>%
  filter(AP_o == ap & claim_type == ct) %>%
  filter(row_number() == 1) %>%
  select(group_o)

plot(
  resurv_fit_predict_m,
  granularity = "output",
  color_par = "#a71429",
  title_par = "COX: Accident Month 7 Claim Type 1",
  group_code = 14
)


ct <- 0
ap <- 2

resurv_fit_predict_y$long_triangle_format_out$output_granularity %>%
  filter(AP_o == ap & claim_type == ct) %>%
  filter(row_number() == 1) %>%
  select(group_o)

plot(
  resurv_fit_predict_y,
  granularity = "output",
  color_par = "#FF6A7A",
  title_par = "COX: Accident Year 2 Claim Type 0",
  group_code = 3
)


ct <- 1
ap <- 3

resurv_fit_predict_y$long_triangle_format_out$output_granularity %>%
  filter(AP_o == ap & claim_type == ct) %>%
  filter(row_number() == 1) %>%
  select(group_o)


plot(
  resurv_fit_predict_y,
  granularity = "output",
  color_par = "#FF6A7A",
  title_par = "COX: Accident Year 3 Claim Type 1",
  group_code = 6
)
```


## Code for computing ARE TOT and ARE CAL

The code below can be used to compute the performance metrics in Table 6 of the manuscript. 

```{r eval=FALSE, include=TRUE}

conversion_factor <- individual_data$conversion_factor

max_dp_i <- 1440

true_output <- resurv_fit_cox$IndividualDataPP$full.data %>%
  mutate(
    DP_rev_o = floor(max_dp_i * conversion_factor) -
      ceiling(
              DP_i * conversion_factor +
                ((AP_i - 1) %% (
                  1 / conversion_factor
                )) * conversion_factor) + 1,
    AP_o = ceiling(AP_i * conversion_factor),
    TR_o = AP_o - 1
  ) %>%
  filter(DP_rev_o <= TR_o) %>%
  group_by(claim_type, AP_o, DP_rev_o) %>%
  mutate(claim_type = as.character(claim_type)) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  filter(DP_rev_o > 0)

out_list <- resurv_fit_predict_q$long_triangle_format_out
out <- out_list$output_granularity

#Total output
score_total <- out[, c("claim_type", "AP_o", "DP_o", "expected_counts")] %>%
  mutate(DP_rev_o = 16 - DP_o + 1) %>%
  inner_join(true_output, by = c("claim_type", "AP_o", "DP_rev_o")) %>%
  mutate(ave = I - expected_counts, abs_ave = abs(ave)) %>%
  # from here it is reformulated for the are tot
  ungroup() %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave = abs(sum(ave)), I = sum(I))

are_tot <- sum(score_total$abs_ave) / sum(score_total$I)


dfs_output <- out %>%
  mutate(DP_rev_o = 16 - DP_o + 1) %>%
  select(AP_o, claim_type, DP_rev_o, f_o) %>%
  mutate(DP_rev_o = DP_rev_o) %>%
  distinct()

#Cashflow on output scale.Etc quarterly cashflow development
score_diagonal <- resurv_fit_cox$IndividualDataPP$full.data  %>%
  mutate(
    DP_rev_o = floor(max_dp_i * conversion_factor) -
      ceiling(
              DP_i * conversion_factor +
                ((AP_i - 1) %% (
                  1 / conversion_factor
                )) * conversion_factor) + 1,
    AP_o = ceiling(AP_i * conversion_factor)
  ) %>%
  group_by(claim_type, AP_o, DP_rev_o) %>%
  mutate(claim_type = as.character(claim_type)) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(claim_type, AP_o) %>%
  arrange(desc(DP_rev_o)) %>%
  mutate(I_cum = cumsum(I)) %>%
  mutate(I_cum_lag = lag(I_cum, default = 0)) %>%
  left_join(dfs_output, by = c("AP_o", "claim_type", "DP_rev_o")) %>%
  mutate(I_cum_hat =  I_cum_lag * f_o,
         RP_o = max(DP_rev_o) - DP_rev_o + AP_o) %>%
  inner_join(true_output[, c("AP_o", "DP_rev_o")] %>%  distinct()
             , by = c("AP_o", "DP_rev_o")) %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave2_diag = abs(sum(I_cum_hat) - sum(I_cum)), I = sum(I))

are_cal_q <- sum(score_diagonal$abs_ave2_diag) / sum(score_diagonal$I)


# scoring XGB ----

out_xgb <- resurv_predict_xgb$long_triangle_format_out$output_granularity

score_total_xgb <- out_xgb[, c("claim_type",
                               "AP_o",
                               "DP_o",
                               "expected_counts")] %>%
  mutate(DP_rev_o = 16 - DP_o + 1) %>%
  inner_join(true_output, by = c("claim_type", "AP_o", "DP_rev_o")) %>%
  mutate(ave = I - expected_counts, abs_ave = abs(ave)) %>%
  # from here it is reformulated for the are tot
  ungroup() %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave = abs(sum(ave)), I = sum(I))

are_tot_xgb <- sum(score_total_xgb$abs_ave) / sum(score_total$I)


dfs_output_xgb <- out_xgb %>%
  mutate(DP_rev_o = 16 - DP_o + 1) %>%
  select(AP_o, claim_type, DP_rev_o, f_o) %>%
  mutate(DP_rev_o = DP_rev_o) %>%
  distinct()

#Cashflow on output scale.Etc quarterly cashflow development
score_diagonal_xgb <- resurv_fit_cox$IndividualDataPP$full.data  %>%
  mutate(
    DP_rev_o = floor(max_dp_i * conversion_factor) -
      ceiling(
              DP_i * conversion_factor +
                ((AP_i - 1) %% (
                  1 / conversion_factor
                )) * conversion_factor) + 1,
    AP_o = ceiling(AP_i * conversion_factor)
  ) %>%
  group_by(claim_type, AP_o, DP_rev_o) %>%
  mutate(claim_type = as.character(claim_type)) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(claim_type, AP_o) %>%
  arrange(desc(DP_rev_o)) %>%
  mutate(I_cum = cumsum(I)) %>%
  mutate(I_cum_lag = lag(I_cum, default = 0)) %>%
  left_join(dfs_output_xgb, by = c("AP_o", "claim_type", "DP_rev_o")) %>%
  mutate(I_cum_hat =  I_cum_lag * f_o,
         RP_o = max(DP_rev_o) - DP_rev_o + AP_o) %>%
  inner_join(true_output[, c("AP_o", "DP_rev_o")] %>%  distinct()
             , by = c("AP_o", "DP_rev_o")) %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave2_diag = abs(sum(I_cum_hat) - sum(I_cum)), I = sum(I))

are_cal_q_xgb <- sum(score_diagonal_xgb$abs_ave2_diag) / sum(score_diagonal$I)

# scoring NN ----

out_nn <- resurv_predict_nn$long_triangle_format_out$output_granularity

score_total_nn <- out_nn[, c("claim_type",
                             "AP_o",
                             "DP_o",
                             "expected_counts")] %>%
  mutate(DP_rev_o = 16 - DP_o + 1) %>%
  inner_join(true_output, by = c("claim_type", "AP_o", "DP_rev_o")) %>%
  mutate(ave = I - expected_counts, abs_ave = abs(ave)) %>%
  # from here it is reformulated for the are tot
  ungroup() %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave = abs(sum(ave)), I = sum(I))

are_tot_nn <- sum(score_total_nn$abs_ave) / sum(score_total$I)


dfs_output_nn <- out_nn %>%
  mutate(DP_rev_o = 16 - DP_o + 1) %>%
  select(AP_o, claim_type, DP_rev_o, f_o) %>%
  mutate(DP_rev_o = DP_rev_o) %>%
  distinct()

#Cashflow on output scale.Etc quarterly cashflow development
score_diagonal_nn <- resurv_fit_cox$IndividualDataPP$full.data  %>%
  mutate(
    DP_rev_o = floor(max_dp_i * conversion_factor) -
      ceiling(
              DP_i * conversion_factor +
                ((AP_i - 1) %% (
                  1 / conversion_factor
                )) * conversion_factor) + 1,
    AP_o = ceiling(AP_i * conversion_factor)
  ) %>%
  group_by(claim_type, AP_o, DP_rev_o) %>%
  mutate(claim_type = as.character(claim_type)) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(claim_type, AP_o) %>%
  arrange(desc(DP_rev_o)) %>%
  mutate(I_cum = cumsum(I)) %>%
  mutate(I_cum_lag = lag(I_cum, default = 0)) %>%
  left_join(dfs_output_nn, by = c("AP_o", "claim_type", "DP_rev_o")) %>%
  mutate(I_cum_hat =  I_cum_lag * f_o,
         RP_o = max(DP_rev_o) - DP_rev_o + AP_o) %>%
  inner_join(true_output[, c("AP_o", "DP_rev_o")] %>%  distinct()
             , by = c("AP_o", "DP_rev_o")) %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave2_diag = abs(sum(I_cum_hat) - sum(I_cum)), I = sum(I))

are_cal_q_nn <- sum(score_diagonal_nn$abs_ave2_diag) / sum(score_diagonal$I)

# Scoring Chain-Ladder ----

true_output_cl <- individual_data$full.data %>%
  mutate(
    DP_rev_o = floor(max_dp_i * conversion_factor) -
      ceiling(
              DP_i * conversion_factor +
                ((AP_i - 1) %% (
                  1 / conversion_factor
                )) * conversion_factor) + 1,
    AP_o = ceiling(AP_i * conversion_factor),
    TR_o = AP_o - 1
  ) %>%
  filter(DP_rev_o <= TR_o) %>%
  mutate(DP_o = max(individual_data$training.data$DP_rev_o) - DP_rev_o + 1) %>%
  group_by(AP_o, DP_o, DP_rev_o) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  filter(DP_rev_o > 0)
latest_observed <- individual_data$training.data %>%
  filter(DP_rev_o >= TR_o) %>%
  mutate(DP_o = max(individual_data$training.data$DP_rev_o) - DP_rev_o + 1) %>%
  group_by(AP_o) %>%
  mutate(DP_max = max(DP_o)) %>%
  group_by(AP_o, DP_max) %>%
  summarize(I = sum(I), .groups = "drop")

clmodel <- individual_data$training.data %>%
  mutate(DP_o = max(individual_data$training.data$DP_rev_o) - DP_rev_o + 1) %>%
  group_by(AP_o, DP_o) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(AP_o) %>%
  arrange(DP_o) %>%
  mutate(I_cum = cumsum(I), I_cum_lag = lag(I_cum, default = 0)) %>%
  ungroup() %>%
  group_by(DP_o) %>%
  reframe(df = sum(I_cum * (
    AP_o <= max(individual_data$training.data$AP_o) - DP_o + 1
  )) /
    sum(I_cum_lag * (
      AP_o <= max(individual_data$training.data$AP_o) - DP_o + 1
    )), I = sum(I * (
    AP_o <= max(individual_data$training.data$AP_o) - DP_o
  ))) %>%
  mutate(DP_o_join = DP_o) %>%
  mutate(DP_rev_o = max(DP_o) - DP_o + 1)

predictions <- expand.grid(AP_o = latest_observed$AP_o,
                           DP_o = clmodel$DP_o_join) %>%
  left_join(clmodel[, c("DP_o_join", "df")], by = c("DP_o" = "DP_o_join")) %>%
  left_join(latest_observed, by = "AP_o") %>%
  rowwise() %>%
  filter(DP_o > DP_max) %>%
  ungroup() %>%
  group_by(AP_o) %>%
  arrange(DP_o) %>%
  mutate(df_cum = cumprod(df)) %>%
  mutate(I_expected = I * df_cum - I * lag(df_cum, default = 1)) %>%
  select(DP_o, AP_o, I_expected)

conversion_factor <- individual_data$conversion_factor
max_dp_i <- 1440
score_total <- predictions  %>%
  inner_join(true_output_cl, by = c("AP_o", "DP_o")) %>%
  mutate(ave = I - I_expected, abs_ave = abs(ave)) %>%
  # from here it is reformulated for the are tot
  ungroup() %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave = abs(sum(ave)), I = sum(I))

are_tot <- sum(score_total$abs_ave) / sum(score_total$I)

score_diagonal <- individual_data$full.data  %>%
  mutate(
    DP_rev_o = floor(max_dp_i * conversion_factor) -
      ceiling(
              DP_i * conversion_factor +
                ((AP_i - 1) %% (
                  1 / conversion_factor
                )) * conversion_factor) + 1,
    AP_o = ceiling(AP_i * conversion_factor)
  ) %>%
  group_by(claim_type, AP_o, DP_rev_o) %>%
  mutate(claim_type = as.character(claim_type)) %>%
  summarize(I = sum(I), .groups = "drop") %>%
  group_by(claim_type, AP_o) %>%
  arrange(desc(DP_rev_o)) %>%
  mutate(I_cum = cumsum(I)) %>%
  mutate(I_cum_lag = lag(I_cum, default = 0)) %>%
  mutate(DP_o = max(individual_data$training.data$DP_rev_o) - DP_rev_o + 1) %>%
  left_join(CL[, c("DP_o", "df")], by = c("DP_o")) %>%
  mutate(I_cum_hat =  I_cum_lag * df,
         RP_o = max(DP_rev_o) - DP_rev_o + AP_o) %>%
  inner_join(true_output_cl[, c("AP_o", "DP_rev_o")] %>%  distinct()
             , by = c("AP_o", "DP_rev_o")) %>%
  group_by(AP_o, DP_rev_o) %>%
  reframe(abs_ave2_diag = abs(sum(I_cum_hat) - sum(I_cum)), I = sum(I))

are_cal_q <- sum(score_diagonal$abs_ave2_diag) / sum(score_diagonal$I)

```




