---
title: "Getting started with ReSurv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with ReSurv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(ReSurv)
```

ReSurv estimates IBNR claim counts using reverse-time proportional hazard
models. The following small example runs during package checks.

## Prepare individual claims

```{r data}
claims <- data_generator(
  random_seed = 1964, scenario = "alpha", time_unit = 1,
  years = 4, period_exposure = 100
)
individual <- IndividualDataPP(
  claims, categorical_features = "claim_type",
  accident_period = "AP", calendar_period = "RP",
  input_time_granularity = "years", output_time_granularity = "years",
  years = 4
)
head(individual$training.data)
```

Each row represents a claim. `accident_period` and `calendar_period` name the
accident and reporting columns. Supply `id` to retain only the first row per
identifier. Continuous and categorical features are specified by column name.
`continuous_features_spline` selects continuous features to smooth in Cox models.

Supported time units are days, months, quarters, semesters, and years. Output
units must be equal to or coarser than input units and permit exact grouping.
The horizon is `years`; when omitted it is inferred from development times.
For a known valuation horizon, specify it explicitly. `training.data` contains
observed upper-triangle rows, `full.data` contains all encoded rows, and
`data_information` stores formulas, features, and time-scale metadata.

## Fit and predict

```{r cox}
fit <- ReSurv(individual, hazard_model = "COX", eta = 0)
prediction <- predict(fit)
summary(prediction)
head(predictReserve(fit, granularity = "output"))
```

`eta` controls the baseline and hazard-to-development-factor conversion and lies
in [0, 1]; its default is 0.5. The example uses 0. Predictions are counts, not
monetary amounts. `predictReserve()` returns `AP`, `DP`, `CP`, and `IBNR` with
`CP = AP + DP - 1`. Use `granularity = "input"` for the original time scale.
`predict()` provides fuller results, including `predicted_counts` and
`long_triangle_format_out`; set `lower_triangular_output = TRUE` for matrices.

## Tune an XGBoost model

Cross-validation uses sequential folds and returns the best parameter list;
the final model is fitted separately. This short example uses only two boosting
rounds to demonstrate the API, rather than to select a production model.

```{r xgb}
cv <- ReSurvCV(
  individual, model = "XGB",
  hparameters_grid = list(
    booster = "gbtree", eta = c(0.05, 0.1), max_depth = 1,
    subsample = 1, alpha = 0, lambda = 1, min_child_weight = 0,
    nthread = 1
  ),
  folds = 2, random_seed = 1, nrounds = 2
)
cv$out.cv.best.oos
xgb_fit <- ReSurv(
  individual, hazard_model = "XGB", eta = 0,
  hparameters = cv$hparameters.best
)
predict(xgb_fit)$predicted_counts
```

The XGBoost grid's `eta` is its learning rate; the `eta` argument to `ReSurv()`
controls the development-factor conversion. `cv_data_subsample` optionally
reduces the rows used for cross-validation: 0.1 uses ten percent, while 1 uses
all rows. Refit on the full preprocessed data after selection.

## Neural networks

NN models require the optional R package `torch` and its runtime. Install these
once with `install.packages("torch")` and `torch::install_torch()`.
The example below is not run when building the vignette because runtime
installation is a separate user action.

```{r nn, eval=FALSE}
nn_fit <- ReSurv(
  individual, hazard_model = "NN", eta = 0,
  hparameters = list(
    num_layers = 1, num_nodes = 8, activation = "relu",
    optim = "Adam", lr = 0.01, xi = 0.5, eps = 0,
    early_stopping = TRUE, patience = 5, epochs = 20,
    verbose = FALSE, num_workers = 0
  )
)
predictReserve(nn_fit)
```

## Evaluate realized counts

Use `Score_Reserving(models = list(COX = fit), newdata = realized_claims)` when
the lower-triangle outcomes are available. `newdata` may contain individual
claims with the original accident/reporting columns, or an aggregate table
with `AP`, `DP`, `CP`, and `actual` counts on the requested granularity scale.
Metrics include `EI`, `R-tot`, `R-cell-wise`, `R-cal-wise`, and optionally
`CRPS`. The default includes a chain-ladder benchmark; `clmplus_benchmark =
c("ac", "apc")` additionally requires the optional `clmplus` package.
