---
title: "A simple case study"
author: "Gabriele Pittarello"
date: "2023-10-05"
output: html_document
bibliography: references.bib  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ReSurv)
library(data.table)
```


```{r}

beta=2*30
lambda=0.1 #1
k=1
b=1440
alpha=0.5
beta0 = 1.15129
beta1 = 1.95601

F_correct <- function(t, alpha, beta, lambda, k,b,beta_coef){
  #nu/xi*(t/xi)^(nu-1)
  #exp(-(t/xi)^nu)/(1-exp(-(t/xi)^nu)*
  #nu/xi*(t/xi)^(nu-1)*exp(beta1)
  exp(-beta^alpha *(lambda*exp(beta_coef)^(1/(alpha*k)) )^(alpha*k)*(t^(-alpha*k)-b^(-alpha*k)) )
}

c_correct_grouped<-c()
for (i in 0:(b-1)){
  t<-seq(i,i+1, by=0.001)
  n_t<-length(t)
  c_correct_grouped[i+1] <- sum(1-F_correct(t, alpha,beta,lambda,k,b, beta0) )/n_t
}
c_correct_grouped<-c(1,c_correct_grouped[1:(b-1)])

c_correct_grouped1<-c()
for (i in 0:(b-1)){
  t<-seq(i,i+1, by=0.001)
  n_t<-length(t)
  c_correct_grouped1[i+1] <- sum(1-F_correct(t, alpha,beta,lambda,k,b, beta1) )/n_t
}
c_correct_grouped1<-c(1,c_correct_grouped1[1:(b-1)])

plot_datac0 <- data.table(time=(b-1)-seq(0,(b-1),by=1)+1, true =1-c_correct_grouped)[order(time),]
plot_datac1 <- data.table(time=(b-1)-seq(0,(b-1),by=1)+1, true =1-c_correct_grouped1)[order(time),]


real_cty <- data.table(DP_rev_i=rep((b-1)-seq(0,(b-1),by=1)+1,2),
                       claim_type=rep(c("0","1"),each=b),
                       true =c(1-c_correct_grouped,1-c_correct_grouped1))


```



# Introduction

In this vignette we want to generate a data set from scenario Alpha described in @hiabu23 and using COX to fit and predict future IBNR. Below, we describe the data set covariates.

| Covariates                                       | Description        |
|--------------------------------------------------|--------------------|
| `claim_number`                                   | Policy identifier. |
| `claim_type` $\in  \left\{0, 1 \right\}$         | Type of claim.     |
| `AM`                                             | Accident month.    |
| `RM`                                             | Reporting month.   |
| `DM`                                             | Development month. |


The data are simulated on a daily grid, over a four years time horizon with a daily exposure of $200$ claims.

```{r eval=FALSE, include=TRUE}
# Input data

input_data0 <- data_generator(random_seed = 1964,
                              scenario=0,
                              time_unit = 1/360,
                              years = 4,
                              yearly_exposure = 200)

```

In the pre-processing of the data, we specify `claim_type`, as a categorical feature and `AP` as a continuous feature. The calendar period of reporting is `RP`. The input data granularity is `"days"` and we want quarterly predictions (we set `output_time_granularity` to `"quarters"`. The time horizon is $4$ years.

```{r eval=FALSE, include=TRUE}
individual_data <- IndividualData(data = input_data0,
                                  categorical_features = c("claim_type"),
                                  continuous_features = "AP",
                                  accident_period="AP",
                                  calendar_period="RP",
                                  input_time_granularity = "days",
                                  output_time_granularity = "quarters",
                                  years=4)
```

```{r eval=FALSE, include=TRUE}
resurv.fit.cox <- ReSurv(individual_data,
                         hazard_model = "cox")
```

## Model the survival function (COX model)

```{r}

hazard_frame_updatedCX <- resurv.fit.cox$hazard_frame

dt_totCX <- merge(hazard_frame_updatedCX,
                real_cty,
                all=T)

```
```{r}
tmp <- dt_totCX %>%
  filter(claim_type==1, AP_i==1400) %>%
  select(S_i,true,DP_rev_i,claim_type)

tmp<- tmp %>% pivot_longer(cols=c('S_i','true'),
                     names_to = c('curve'),
                     values_to = c('SF'))




```
```{r}
dt_totCX
```

```{r}
ggplot(tmp, aes(x=DP_rev_i,
                y=SF,
                color=curve))+
  geom_line()
```



# eXtreme Gradient Boosting

```{r}
hp_scenario_alpha_xgb <- list(params=list(booster="gbtree",
                                          eta=0.9887265,
                                          subsample=0.7924135 ,
                                          alpha=10.85342,
                                          lambda=6.213317,
                                          min_child_weight=3.042204,
                                          max_depth = 1),
                                          print_every_n = 0,
                                          nrounds=3000,
                                          verbose=F,
                                          early_stopping_rounds = 500)

```


```{r}
resurv.model.xgb.A <-  ReSurv(individual_data,
                              hazard_model = "xgboost",
                              hparameters=hp_scenario_alpha_xgb)
```



```{r}

hazard_frame_updatedXGB <- resurv.model.xgb.A$hazard_frame

dt_tot <- merge(hazard_frame_updatedXGB,
                real_cty,
                all=T)

```

```{r}
tmp <- dt_tot %>%
  filter(claim_type==1, AP_i==13) %>%
  select(S_i,true,DP_rev_i,claim_type)

tmp<- tmp %>% pivot_longer(cols=c('S_i','true'),
                     names_to = c('curve'),
                     values_to = c('SF'))




```
```{r}
dt_tot
```

```{r}
ggplot(tmp, aes(x=DP_rev_i,
                y=SF,
                color=curve))+
  geom_line()
```









